Measurement Bias from Address Aliasing

### 2014-05-17 paper.tex
Improve allocator results
Fullwidth table and updated makefile for producing results

\begin{table*}[t]
  \caption{Addresses returned by different heap allocators when allocating pairs of equally sized buffers.}
  \label{tab:mallocompare}

  %\renewcommand{\tabcolsep}{3pt} % Less padding between cells
  \pgfplotstabletypeset[
    font=\small,
    col sep=comma,
    string type,
    columns={Allocation, 64, 1024, 5120, 1048576},
    column type=r,
    columns/.style={
        width=1cm
    },
    columns/Allocation/.style={
      string type, 
      column type=l
    },
    every head row/.style={
      output empty row,
      before row={\toprule
         & 64 & 1024 & 5120 & 1048576 \\
        },
      after row=\midrule,
    },
    every last row/.style={after row=\bottomrule}
  ]{bin/malloc-comparison.csv}
\end{table*}

>>>>

\begin{table*}[t]
  \caption{Addresses returned by different heap allocators when allocating pairs of equally sized buffers.}
  \label{tab:mallocompare}
  \pgfplotstabletypeset[
    font=\small,
    col sep=comma,
    string type,
    columns={Allocation, 64, 1024, 65536, 1048576, 4194304},
    column type=r,
    columns/Allocation/.style={
      string type, 
      column type=l
    },
    every head row/.style={
      output empty row,
      before row={\toprule
         & 64 B & 1,024 B & 65,536 B & 1,048,576 B & 4,194,304 B \\
        },
      after row=\midrule,
    },
    every odd row/.style={after row=\midrule},
    every last row/.style={after row=\bottomrule}
  ]{bin/malloc-comparison.csv}
\end{table*}
